The Unintended Consequences of Energy Reduction

### 2024-02-14 paper/paper.qmd
weaknesses and next steps added, pls review

---
title: "The Unintended Consequences of Energy Reduction"
subtitle: "How an Act of Environmental Protection Led to the Deaths of Many"
author:
  - Alex Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
pdf-engine: pdflatex
format:
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
include: false
warning: false
message: false
number-sections: true
bibliography: references.bib
---

@@

Weaknesses and next steps should also be included.

>>>>

---
title: "The Unintended Consequences of Energy Reduction"
subtitle: "How an Act of Environmental Protection Led to the Deaths of Many"
author:
  - Yi Fei Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
pdf-engine: pdflatex
format:
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
include: false
warning: false
message: false
number-sections: true
bibliography: references.bib
---

@@

A few weaknesses with the analysis comes from the limitation of data.The scope of analysis for the post-Fukushima incident and the effects of the energy policy is only Japan. There is no comparison to other countries and their markets trends after nuclear accidents such as Ukraine with the Chernobyl incident. Furthermore, the data is limited only from the Fukushima incident up until 2016 allowing for a short term analysis. The physical effects of nuclear incidents along with the economic effects of the energy policy are both issues that can use a more long term approach. Additionally, there is a lack of robustness as the analysis is fixated on the effects caused by the transition from nuclear energy to fossil fuels. However, there are other energy sources such as renewable energy which includes solar and wind energy that should be taken into consideration.

The next steps would be to find more recent data. As aforementioned, the datasets only extend until 2016 and to complete a long-term analysis, more recent Japanese energy data needs to be collected. Moreover, data from before and after other global nuclear incidents should be gathered and evalauted in comparison to Fukushima to evaluate whether the Japanese government's apporoach was the most optimal. Another step that can be taken to futher the analysis could be to explore more granular effects. For example, in addition to looking at how temperatures and strokes can be correlated (pls verify we did this?), other factors such as energy price variation and seasons or energy jobs and employment rates can be observed as well.
